\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}

\title{PS1}
\author{Vladimir Garcia}
\date{January 2018}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle

\section{Summary}
I became interested in economics when I took my first microeconomics class at OU when I was a freshman. It was not as easy as other class I had taken so far, and it made me realize how much I ignored about the topic. The summer after my freshman year I spent it mostly reading more works by economists and financial/econ articles from newspapers. In a way, I continued studying economics to challenge myself and I ended up liking it. I added it as a second major in my Sophomore year. 

I think Big Data is revolutionizing the way we understand societies, and having a better understanding of it is crucial in the labor market and even in the social sciences. Having the chance to learn about Big Data and Machine Learning from the scope of economics was my main motivation to take this class. 

For the final project, I would like to study the influence of Global Warming shocks in the spread of vector-borne diseases (dengue, malaria, etc.) in tropical countries, which is a research idea I have briefly been working on. My main goal for the class is to have a better understanding of machine learning, since it is something I am new to, and learn how to use economic theory and Big Data together. About my plans for after graduation, I am hoping to get into a Masters or PhD program in Economics with an emphasis on economic growth or economic development, or look for summer schools and internships as I try applying again for the next academic year. 

\section{Equation}
\begin{equation}
    a^2+b^2=c^2
\end{equation}
\end{document}
